\documentclass[12pt]{article}
\usepackage[a4paper, total={6.5in, 9in},margin={.5in}]{geometry}
\pagenumbering{gobble}
\usepackage{changepage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage{enumitem}
\setlist[itemize]{noitemsep}
\titlespacing\section{-5pt}{-7pt}{0pt}

\titlespacing\subsection{9pt}{0pt}{3pt}

\begin{document}



{\fontfamily{phv}\selectfont

\section*{\center{Gabriel Brookman}}
\begin{center}\textbf{(208) 904-1760 | brookmangabriel@gmail.com | \href{https://github.com/redless}{github.com/redless}}\end{center}
\section*{Education}

\subsection*{University of Massachusetts Amherst \hfill September 2020-Present} 
  \begin{itemize}

  \item Computer Science MS/PhD. Student. 4.0 GPA. Looking to exit.
\item
  Relevant Coursework: Machine Learning, Natural Language Processing, Probabilistic Graphical Models (ongoing).

\end{itemize}

  \subsection*{Carleton College \hfill September 2016-June 2020} 
  \begin{itemize}

  \item Computer Science Major, Math Minor. In-major GPA: 4.0
\item
  Relevant Coursework: Advanced Algorithms, Advanced Linear Algebra, Algorithms, Applied Regression Analysis, Artificial Intelligence, Calculus Series, Computability and Complexity, Computational Models of Cognition, Data Structures, Linear Algebra, Math of Computer Science, Numerical Analysis, Ordinary Differential Equations, Organization and
  Architecture, Probability, Programming Languages, Quantum Computing, Software Design.
  
    %\item GPA: 4.0 (Comp. Sci.), 3.7 (Overall), 3.8 (Relevant Coursework, see below)
%\item GPA in-major: 4.0

\end{itemize}

\section*{Research/Internships}

\subsection*{\indent Carleton College \hfill June-August 2019}
\begin{itemize}
\item Applied the Apprentice Learner Architecture to extract malrules from students' algebra solutions.
\item Familiarized myself with an undocumented research codebase for the above.
%\item Read papers on machine learning for educational technologies.
\item Presented at a poster session for the general public.
\end{itemize}

\subsection*{\indent Oak Ridge National Labs \hfill June-August 2018}
\begin{itemize}
\item
  Constructed a convolutional neural network in Keras to identify roads
  in satellite images. Finished
  with \textgreater{}95\% accuracy.

  
 \item Performed a literature review on the same to facilitate design and training.

  \item Presented my work in front of 20+ other researchers at a poster session and wrote a research paper.
\end{itemize}

\subsection*{Sandia National Labs \hfill January-March 2018}
\begin{itemize}
\item
  Analyzed experimentally generated images to detect particles suspended in a matrix using ImageJ scripting.
\item
  Fitted regressions on size, angles, and counts from data generated by
  image analysis.
\item
  Published in Journal of Applied Physics (\href{https://aip.scitation.org/doi/10.1063/1.5022471}{DOI: 10.1063/1.5022471}).
\end{itemize}




\subsection*{\indent Vidscripp \hfill December 2017}
\begin{itemize}
\item
  Developed a web app in JavaScript to visualize Vidscripp's database in collaboration with 4 other interns.
%\item Implemented Google Analytics to monitor the use of Vidscripp's app to inform data-driven product decisions.
\item
  Managed git workflow for a team of 5, taught other interns git.
  \end{itemize}
  \begin{comment}
\section*{Publications}
\begin{itemize}
\item J.A Stewart, G. Brookman, P. Price, M. Franco, W. Ji, K. Hattar, R. Dingreville, 2018. Characterizing single isolated radiation-damage events from molecular dynamics via virtual diffraction methods, Journal of Applied Physics.
\end{itemize}
\end{comment}

\section*{Software}
\subsection*{\indent Programming Languages}
\begin{itemize}
\item
  Python: Very experienced with PyTorch and Numpy. Some experience with Jupyter, MatPlotLib, and Keras.
\item
  Lua: Used LOVE2D to hobby-code several games. %Here is a link to 
  My
  favorite: \href{https://github.com/redless/neonjourney}{Neon Journey}.
  \item Working knowledge of: C, Java, Processing, MATLAB, Scheme, Javascript.
\end{itemize}


\subsection*{\indent Software Tools}
\begin{itemize}
\item
  LaTeX: Wrote my problem sets in college with this. Also this resume. 
  %Almost every paper I wrote in college was written with LaTeX. This resume was too.
\item
  git/GitHub: I use this for all of my hobby coding and internship
  projects. \href{https://github.com/redless}{github.com/redless}.
 \item bash shell/vim: I use these daily to take notes and deal with files.
\end{itemize}

\begin{comment}
\section*{Service \& Other Activities}
\begin{itemize}
\item Grader for Artificial Intelligence (Fall 2019), Computational Models of Cognition (Fall 2018), and Calculus I (Fall 2017).
\item Assisted Carleton College Computer Science department in their faculty search by interviewing and providing feedback on 5 candidates for a tenure track faculty position (Winter 2019).
\item Participated in Konhauser Problem Fest mathematics competition (Winter 2019).
\item Participated in ICM Programming Contest (Fall 2018 and 2017).
\item Helped students work on problems as a Mathematics Lab Assistant (Fall 2017).
\end{itemize}
\end{comment}

\scriptsize
\flushright{\textbf{Generated on \today. \href{https://github.com/redless/resumes}{Current}.}}

%cs competitions?


\end{document}