\documentclass{article}
\usepackage[a4paper, total={6.5in, 9in}]{geometry}
\pagenumbering{gobble}
\usepackage{setspace}
\usepackage{changepage}
\usepackage{titlesec}
\usepackage{hyperref}
\titlespacing\section{0pt}{0pt}{2pt}

\titlespacing\subsection{0pt}{0pt}{6pt}



\begin{document}
\setlength{\parindent}{0cm}

{\fontfamily{tnr}\selectfont

300 North College Street

Northfield, MN 55057

October 1st, 2018

\vspace{5mm}

Kyle Schiller

Director of Research

Silenus Cultures

2640 Bryant St, San Francisco, CA 94110

\doublespacing
\vspace{3mm}

Dear Mr. Schiller:
\setlength{\parindent}{1cm}

I was excited to learn of the externship at Silenus Cultures. I believe that the animal suffering caused by the meat industry is the most immoral thing that humans are doing in the world today, and I want to contribute however I can to put an end to it. I've been a vegan for 4 years and a vegetarian for 11.


Furthermore, Silenus Cultures's approach of creating a superior meat alternative resonates with me. I want people to have every reason choose the corpse-free diet, instead of just the moral one. Eliminating the tradeoff between health, taste, convenience, and ethics is the most effective way to convert more people to vegetarianism and veganism in my opinion.


Thanks to my past internships, I'm already well versed in the day-to-day activities that make up research. For example, during my internship at Oak Ridge National Labs, I found and read many papers in my research area, and independently tested out their approaches to try and solve my problem. Even so, I crave more research experience before graduate school, ideally from a diverse range of settings. In particular, I lack exposure to research in industry, which I would gain from your externship.


In addition, I have considerable experience in software engineering. During my 2017 externship at VidScripp, I picked up enough JavaScript to write a web app in three weeks, and also learned some Golang along the way. As a result of experiences like that one, I can quickly gain proficiency with new software, which would be useful as an extern at Silenus Cultures.


Thank you for considering me for your externship.

\setlength{\parindent}{0cm}
Sincerely,

Gabriel Brookman


\end{document}